---
title: r-tutorials
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Description

This project contains `R` code and data for a series of introductory 
programming and data analysis tutorials with 
the `R` programming language. 

# Installation 

To download and use this code on a windows machine, open the Git Bash terminal 
and clone the repository into directory.  
Try to make sure the directory is something like `~/Projects`, (where `~` signifies the user home directory), 
just so there are no issues with accessing the project. 

To do this process, copy and paste the following lines of code into the git bash 
terminal. 

```{bash, echo=TRUE, eval=FALSE}
$ mkdir ~/Projects # Make a projects directory if it doesn't exist
$ cd ~/Projects # Move to the project directory
$ git clone https://github.com/gden173/r-tutorials.git # Clone the repository into this directory
$ cd r-tutorials # Move into the project directory
```


# Initial Project Setup 

To make sure you have everything installed correctly,  double click on the 
`Rstudio` project file `r-tutorials.Rproj` which will open up `R` studio 
into the project. 

The, go to the `R` console and run the following lines of code 

```{r, echo=TRUE, eval=FALSE}
> install.packages('renv') # R package manager
> renv::hydrate() # Downloads all packages that you will need, all of the same version that I will be using. 
```

This will download and install all the necessary `R` packages that (most likely)
you will ever need, and that will be needed to run this analysis.  
Installation of the `tidyverse` package will take ~10 minutes, so it is better 
to do these steps ahead of time. 

# Project Structure

This project has been structured similar to an `R` package, just so it has all 
the necessary tools for analysis.  All `R` source code will be placed 
in the `R/` directory (we probably won't add anything to this), and all 
data will be placed in the `data/` directory. 

# Tutorial Structure 

The tutorial are placed inside `Rmarkdown` templates. To access these 
templates got to `File > New File > R Markdown`. A box should pop up asking 
about the `R Markdown` configurations that you will like. From here, say that you 
would like to use an `R Markdown` template. After clicking on this option a list 
of templates will be shown, to select the appropriate tutorial click on `r-tutorial_XX`. 

## Tutorial 01 

TODO: Add instructions



# References
```{r}
citation()
```

